|

### 2023-07-07 paper/paper.qmd
Change bent-ratio labs

```{r #fig-bent-ratio}
#| fig-cap: Verdeling van de bent-ratio in de vier provincies
ggplot(distribution, aes(x = bent_ratio)) +
  geom_histogram(bins=10) +
  facet_wrap( ~ dialect)
```

>>>>

```{r #fig-bent-ratio}
#| fig-cap: Verdeling van de bent-ratio in de vier provincies
ggplot(distribution, aes(x = bent_ratio)) +
  geom_histogram(bins=10) +
  facet_wrap( ~ dialect) +
  labs(y= "Aantal attestaties", x = "bent-ratio")
```
